Predicting sales of newly published books

### 2015-11-03 paper.tex
Añadida la tabla de variables a petición de @pacv

\documentclass{llncs}
\usepackage{graphics}
\usepackage{amssymb}
\usepackage[dvips]{epsfig}
\usepackage[latin1]{inputenc}

@@

% con CfsSubsetEval salen seleccionadas (4):
% num_reprints tot_points_sale print_run + total_sales
Using the CfsSubsetEval feature selection method, the following variables have 
been selected: \emph{number of reprints, total points of sale, print-run, total sales}.

@@

Once the different reduced datasets have been obtained, proposed methods 
(M5P, LR, SVM, kNN, MLP) have been selected for this study from 
the Weka implementation, and they were run 30 times with the Weka default parameter 
settings and a different random initialization seed for each run and each dataset.

>>>>

\documentclass{llncs}
\usepackage{graphics}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[dvips]{epsfig}
\usepackage[latin1]{inputenc}

@@

% con CfsSubsetEval salen seleccionadas (4):
% num_reprints tot_points_sale print_run + total_sales
Using the CfsSubsetEval feature selection method, the following variables have 
been selected: \emph{number of reprints, total points of sale, print-run, total sales}.
%FERGU: podeis quitar estos parrafos de variables porque ya está la tabla :)

@@

\begin{table}
\begin{tabular}[htb]{|c|c|c|c|c|}
\hline
Variable  & PreSales & ReliefFAttributeEval  & SOM & CfsSubsetEval \\ \hline \hline
subject1    & $\checkmark$  &   &   &   \\ \hline
subject2    & $\checkmark$  &   &   &   \\ \hline
subject3    & $\checkmark$  &   &   &   \\ \hline
editorial   & $\checkmark$  &   &   &   \\ \hline
collection  & $\checkmark$  &   &   &   \\ \hline
binding   & $\checkmark$  &   &   &   \\ \hline
ret\_pricer    & $\checkmark$  &   & $\checkmark$  &   \\ \hline
reprints    & $\checkmark$  & $\checkmark$  & $\checkmark$  &   \\ \hline
num\_reprints    & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
gifts   & $\checkmark$  &   & $\checkmark$  &   \\ \hline
distrib\_novelty   & $\checkmark$  & $\checkmark$  & $\checkmark$  &   \\ \hline
tot\_points\_sale   & $\checkmark$  & $\checkmark$  &   & $\checkmark$  \\ \hline
tot\_points\_sale\_1st\_year    & $\checkmark$  & $\checkmark$  &   &   \\ \hline
weeks\_sale    & $\checkmark$  & $\checkmark$  &   &   \\ \hline
print\_run   & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
total\_sales   & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline

\end{tabular}
\caption{Variables used in each method.} %PABLO: Poned este caption bien
\label{tab:varmethods}
\end{table}

Table \ref{tab:varmethods} shows the used variables used in each step. %Pablo: poner también esta frase mejor 
Once the different reduced datasets have been obtained, proposed methods 
(M5P, LR, SVM, kNN, MLP) have been selected for this study from 
the Weka implementation, and they were run 30 times with the Weka default parameter 
settings and a different random initialization seed for each run and each dataset.
